Associahedra for finite type cluster algebras \\ and minimal relations between $\b{g}$-vectors

### 2019-07-09 thirdPaper/draft/typeConeAssociahedra.tex

Even though graph associahedra do not have simplicial type cones except for the path (\cref{prop:simplicialnestedfan}), we provide a non-redundant characterization of the type cones of graphical nested fans:

@@

% Schematic diagram:\yann{Vincent, Arnau, je suis certain que vous feriez bien mieux que moi. Puis-je vous demander de le représenter ?}
% 
% I.1 explains the type cone approach to the problem
% 
% This strategy is used in I.2.2 for cluster algebras and in I.2.3 for gentle algebras.
% 
% II.3 cluster categories (2-Calabi--Yau triangulated categories) is used in 1.2.2 for proving U.E.R.P. and simpliciality of the type cone.
% 
% II.4 generalises II.3, is used in I.2.3 for proving the U.E.R.P. and offers a different proof of simpliciality of the type cone .

>>>>

Even though graph associahedra do not have simplicial type cones except for the path (\cref{prop:simplicialnestedfan}), we provide a non-redundant characterization of the type cones of all graphical nested fans:

@@

% Schematic diagram:
\yann{Vincent, Arnau, je suis certain que vous feriez bien mieux que moi. Puis-je vous demander de le représenter ?}
\arnau{As tu une idée en tête de comment le réprsenter? Je trouve que ce que t'as écrit est très clair et je ne vois pas comment faire une schema qui le ameillore}
% 
% I.1 explains the type cone approach to the problem
% 
% This strategy is used in I.2.2 for cluster algebras and in I.2.3 for gentle algebras.
% 
% II.3 cluster categories (2-Calabi--Yau triangulated categories) is used in 1.2.2 for proving U.E.R.P. and simpliciality of the type cone.
% 
% II.4 generalises II.3, is used in I.2.3 for proving the U.E.R.P. and offers a different proof of simpliciality of the type cone .
